|

### 2024-07-12 doc/paper_mine.qmd
final commit

# Display the median residual income table
html_table_filtered = median_residual_income_filtered.to_html(classes='dataframe', border=0)
html_content_filtered = f'<div style="max-width: 80%; margin: auto;">{html_table_filtered}</div>'
from IPython.display import display, HTML
display(HTML(html_content_filtered))
```

>>>>

# Display the median residual income table
html_table_filtered = median_residual_income_filtered.to_html(
    classes='dataframe', 
    border=0
)

html_content_filtered = (
    f'<div style="max-width: 80%; margin: auto;">'
    f'{html_table_filtered}'
    f'</div>'
)
from IPython.display import display, HTML
display(HTML(html_content_filtered))
```
